{\color {red}better title eventually}

### 2015-05-12 cs261n-paper/paper.tex
little fixes

\section{Introduction} %%% 
% \indent \indent Talk about the results and contributions concretely.
% As short as possible summary of UX sprint here. %only what is necessary to understand results. 
% Talk about the changes resulted in the Tor browser here.
% As short as possible summary of lessons learned, 
% and also a short as possible motivation for censorship work here. %yep, same.
% Talk about the experiment design quickly here.

We aim to improve user security by evaluating
and improving the usability of security software.
Both ``usability'' and ``security'' encompass many topics;
therefore we limit our scope and focus on
an important and timely use case:
user configuration of software to evade Internet censorship.
In this report, we detail the design of a usability-focused user experiment,
which we hope will be a benchmark for such studies
and guide their development in the future.

@@

\subsection{Tor} 
% \indent \indent Talk about anything relevant to Tor. Just enough background so
% that people who have never heard of it will know what I am talking
% about, but no more than that.

The Tor Project, known for its anonymity network~\cite{tor-design},
has in recent years become an important player in the world of
censorship circumvention.
In its early days, people used Tor to evade censorship,
and in response censors began to block Tor itself.
In response, work began on various anti-censorship technologies
now known as ``pluggable transports''~\cite{pluggable-transports}.
Currently there are over 15,000 users accessing the Tor network
at any given time using one of these
anti-censorship technologies~\cite{userstats-bridge-country}.

@@

{\color {red} what we will recruit for, how we inform, and interactions.}

@@

\indent\indent This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley. Recruitment will be conducted through Craigslist. 
Although Xlab provides a portal in which researchers can recruit a pre-registered user base,
we choose to not recruit through this portal, as their participants mostly consist of mostly Berkeley 
students. The laboratory setting consists of 36 Toshiba Tecra R850 laptops with cubicle walls 
separating each laptop. Since we do not have the ability to employ network-level firewalls in this
laboratory setting, we will use individual host firewalls to simulate the censorship environments.  
We will write and employ a browser extension will record user activity, such as how many times they 
clicked, what websites they were successfully able to visit, and how long they took to complete 
each task. {\color {red} This is because WHY?} %ask david exactly why--technically. isn't the first hop in the clear?

>>>>

\section{Introduction} %%%

\indent \indent We aim to improve user security by evaluating
and improving the usability of security software.
Both ``usability'' and ``security'' encompass many topics;
therefore we limit our scope and focus on
an important and timely use case:
user configuration of software to evade Internet censorship.
In this report, we detail the design of a usability-focused user experiment,
which we hope will be a benchmark for such studies
and guide their development in the future.

@@

\subsection{Tor}

\indent \indent The Tor Project, known for its anonymity network~\cite{tor-design},
has in recent years become an important player in the world of
censorship circumvention.
In its early days, people used Tor to evade censorship,
and in response censors began to block Tor itself.
In response, work began on various anti-censorship technologies
now known as ``pluggable transports''~\cite{pluggable-transports}.
Currently there are over 15,000 users accessing the Tor network
at any given time using one of these
anti-censorship technologies~\cite{userstats-bridge-country}.

@@

@@

\indent\indent This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley. Recruitment will be conducted through Craigslist. 
Although Xlab provides a portal in which researchers can recruit a pre-registered user base,
we choose to not recruit through this portal, as their participants mostly consist of mostly Berkeley 
students. The laboratory setting consists of 36 Toshiba Tecra R850 laptops with cubicle walls 
separating each laptop. Since we do not have the ability to employ network-level firewalls in this
laboratory setting, we will use individual host firewalls to simulate the censorship environments.  
We will write and employ a browser extension will record user activity, such as how many times they 
clicked, what websites they were successfully able to visit, and how long they took to complete 
each task.
